---
title: "Scouting Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(ggthemes)
library(scales)
library(grid)
library(gridExtra)
library(dplyr)
```

### Reading data
```{r}
analysis <- read.csv("scouting_analysis.csv")
```

```{r}
analysis$Expertise <- ifelse(analysis$Rank == 1, 1, ifelse(analysis$Rank == 2,
                      1, ifelse(analysis$Rank == 3, -1, ifelse(analysis$Rank == 4,
                      2, ifelse(analysis$Rank == 5, 2, ifelse(analysis$Rank
                      == 6, -1, ifelse(analysis$Rank ==7, 3, 0)))))))

bronze_rows = which(analysis$Rank == 1)
silver_rows = which(analysis$Rank == 2)
gold_rows = which(analysis$Rank == 3)
plat_rows = which(analysis$Rank == 4)
diam_rows = which(analysis$Rank == 5)
mast_rows = which(analysis$Rank == 6)
gmast_rows = which(analysis$Rank == 7)

novice_rows = which(analysis$Expertise == 1)
prof_rows = which(analysis$Expertise == 2)
expert_rows = which(analysis$Expertise == 3)

bronze_games <- 843
silver_games <- 6620
gold_games <- 11127
plat_games <- 21484
diam_games <- 26989
mast_games <- 7790
gmast_games <- 2519

novice_games <- bronze_games + silver_games
prof_games <- plat_games + diam_games
expert_games <- gmast_games

bronze_col <- "#4d4dff"
silver_col <- "#36b3b3"
gold_col <- "#884dff"
plat_col <- "#00e5e6"
diam_col <- "#3655b3"
mast_col <- "#000066"
gmast_col <- "#3c00b3"

novice_col <- "#4d4dff"
prof_col <- "#36b3b3"
expert_col <- "#884dff"
```

```{r}
Rank <- c("1-Bronze", "2-Silver", "3-Gold", "4-Platinum", "5-Diamond", "6-Master", "7-Grandmaster")
InitialScouting <- c(0.7093712930011863, 0.7737160120845922, 0.8616877864653545, 0.9266896294917147, 0.9281559153729297, 0.9359435173299101, 0.9475982532751092)
Expansions <- c(0.7390272835112692, 0.7468277945619335, 0.7697492585602588, 0.7978495624650903, 0.796250324206158, 0.7793324775353017, 0.7610162763001191)
NewAreas <- c(0.2680901542111507, 0.31435045317220545, 0.35094814415386, 0.37027555390057715, 0.4673014932009337, 0.5205391527599487, 0.6081778483525209)
BetweenBattles <- c(0.4887307236061684, 0.5288519637462236, 0.5355441718342769, 0.5382144851982871, 0.5919078142947126, 0.6138639281129653, 0.6375545851528385)

perc_rank <- data.frame(Rank, InitialScouting, Expansions, NewAreas, BetweenBattles)

Expertise <- c("1-Novice", "2-Proficient", "3-Expert")
InitialScouting <- c(0.7923608649415101, 0.9213611948120005, 0.9438694267515924)
Expansions <- c(0.7462779156327544, 0.7934789728809118, 0.7716958598726115)
NewAreas <- c(0.32665721375398793, 0.42003471767326084, 0.6033041401273885)
BetweenBattles <- c(0.5293335696561503, 0.5667168872003144, 0.6407245222929936)

perc_expertise <- data.frame(Expertise, InitialScouting, Expansions, NewAreas, BetweenBattles)

rank_cols <- c("1-Bronze"=bronze_col, "2-Silver"=silver_col, "3-Gold"=gold_col,
            "4-Platinum"=plat_col, "5-Diamond"=diam_col, "6-Master"=mast_col, "7-Grandmaster"=gmast_col)
expertise_cols <- c("1-Novice"=novice_col, "2-Proficient"=prof_col,"3-Expert"=expert_col)
```


### Distribution of Scouting Categories for each rank, normalized by % of Matches
```{r}
bronze_cats <- ggplot(analysis[bronze_rows,], aes(x = Category)) +
                geom_histogram(aes(y=(..count..)/(bronze_games )), color=bronze_col, fill=bronze_col,
                binwidth = 1, alpha = 0.4) + labs(y="% of Matches", x = "Scouting Category") + 
                coord_cartesian(ylim =c(0, 1),xlim = c(1,4))+ scale_y_continuous(labels=scales::percent)
silver_cats <- ggplot(analysis[silver_rows,], aes(x = Category)) +
                geom_histogram(aes(y=(..count..)/(silver_games )), color=silver_col, fill=silver_col,
                binwidth = 1, alpha = 0.4) + labs(y=" ", x = "Scouting Category") + 
                coord_cartesian(ylim =c(0, 1),xlim = c(1,4))+ scale_y_continuous(labels=scales::percent)
gold_cats <- ggplot(analysis[gold_rows,], aes(x = Category)) +
                geom_histogram(aes(y=(..count..)/(gold_games )), color=gold_col, fill=gold_col,
                binwidth = 1, alpha = 0.4) + labs(y=" ", x = "Scouting Category") + 
                coord_cartesian(ylim =c(0, 1),xlim = c(1,4))+ scale_y_continuous(labels=scales::percent)
plat_cats <- ggplot(analysis[plat_rows,], aes(x = Category)) +
                geom_histogram(aes(y=(..count..)/(plat_games )), color=plat_col, fill=plat_col,
                binwidth = 1, alpha = 0.4) + labs(y="% of Matches", x = "Scouting Category") + 
                coord_cartesian(ylim =c(0, 1),xlim = c(1,4))+ scale_y_continuous(labels=scales::percent)
diam_cats <- ggplot(analysis[diam_rows,], aes(x = Category)) +
                geom_histogram(aes(y=(..count..)/(diam_games )), color=diam_col, fill=diam_col,
                binwidth = 1, alpha = 0.4) + labs(y=" ", x = "Scouting Category") + 
                coord_cartesian(ylim =c(0, 1),xlim = c(1,4))+ scale_y_continuous(labels=scales::percent)
mast_cats <- ggplot(analysis[mast_rows,], aes(x = Category)) +
                geom_histogram(aes(y=(..count..)/(mast_games )), color=mast_col, fill=mast_col,
                binwidth = 1, alpha = 0.4) + labs(y=" ", x = "Scouting Category") + 
                coord_cartesian(ylim =c(0, 1),xlim = c(1,4))+ scale_y_continuous(labels=scales::percent)
gmast_cats <- ggplot(analysis[gmast_rows,], aes(x = Category)) +
                geom_histogram(aes(y=(..count..)/(gmast_games )), color=gmast_col, fill=gmast_col,
                binwidth = 1, alpha = 0.4) + labs(y="% of Matches", x = "Scouting Category") + 
                coord_cartesian(ylim =c(0, 1),xlim = c(1,4))+ scale_y_continuous(labels=scales::percent)

title <- textGrob("Percentage of Matches in each Scouting Category for each Rank",
                   gp=gpar(fontsize=11,font=3))

grid.arrange(bronze_cats, silver_cats, gold_cats, plat_cats, diam_cats, mast_cats, gmast_cats, ncol=3, nrow=3, top = title)
```

### Scouting categories per Expertise
```{r}
novice_cats <- ggplot(analysis[novice_rows,], aes(x = Category)) +
                geom_histogram(aes(y=(..count..)/(novice_games )), color=novice_col, fill=novice_col,
                binwidth = 1, alpha = 0.4) + labs(y="% of Matches", x = "Scouting Category") + 
                coord_cartesian(ylim =c(0, 1),xlim = c(1,4))+ scale_y_continuous(labels=scales::percent)
prof_cats <- ggplot(analysis[prof_rows,], aes(x = Category)) +
                geom_histogram(aes(y=(..count..)/(prof_games )), color=prof_col, fill=prof_col,
                binwidth = 1, alpha = 0.4) + labs(y=" ", x = "Scouting Category") + 
                coord_cartesian(ylim =c(0, 1),xlim = c(1,4))+ scale_y_continuous(labels=scales::percent)
expert_cats <- ggplot(analysis[expert_rows,], aes(x = Category)) +
                geom_histogram(aes(y=(..count..)/(expert_games )), color=expert_col, fill=expert_col,
                binwidth = 1, alpha = 0.4) + labs(y=" ", x = "Scouting Category") + 
                coord_cartesian(ylim =c(0, 1),xlim = c(1,4))+ scale_y_continuous(labels=scales::percent)

title2 <- textGrob("Percentage of Matches in each Scouting Category for each Level of Expertise",
                   gp=gpar(fontsize=11,font=3))
grid.arrange(novice_cats, prof_cats, expert_cats, ncol=3, nrow=1, top = title2)
```


### Distribution of Initial Scouting for each rank, normalized by % of Matches
```{r}
bronze_init <- ggplot(analysis[bronze_rows,], aes(x = InitialScouting)) +
                geom_bar(aes(y=(..count..)/(bronze_games)), color=bronze_col, fill=bronze_col,
                alpha = 0.4) + labs(y="% of Matches") + 
                coord_cartesian(ylim =c(0,1),xlim=c(-0.5,1.5))+ scale_y_continuous(labels=scales::percent) +
                scale_x_continuous(name = "Bronze", breaks = c(0, 1), labels = c(
                "Not Present", "Present"))

silver_init <- ggplot(analysis[silver_rows,], aes(x = InitialScouting)) +
                geom_bar(aes(y=(..count..)/(silver_games )), color=silver_col, fill=silver_col,
                alpha = 0.4) + labs(y=" ") +coord_cartesian(ylim =c(0, 1),xlim = c(-0.5,1.5))+
                scale_y_continuous(labels=scales::percent)+
                scale_x_continuous(name = "Silver", breaks = c(0, 1), labels = c(
                "Not Present", "Present"))

gold_init <- ggplot(analysis[gold_rows,], aes(x = InitialScouting)) +
                geom_bar(aes(y=(..count..)/(gold_games )), color=gold_col, fill=gold_col,
                alpha = 0.4) + labs(y=" ") + coord_cartesian(ylim =c(0, 1),xlim = c(-0.5,1.5))+
                scale_y_continuous(labels=scales::percent)+
                scale_x_continuous(name = "Gold", breaks = c(0, 1), labels = c(
                "Not Present", "Present"))

plat_init <- ggplot(analysis[plat_rows,], aes(x = InitialScouting)) +
                geom_bar(aes(y=(..count..)/(plat_games )), color=plat_col, fill=plat_col,
                alpha = 0.4) + labs(y="% of Matches") + coord_cartesian(ylim =c(0, 1),xlim = c(-0.5,1.5))+
                scale_y_continuous(labels=scales::percent)+
                scale_x_continuous(name = "Platinum", breaks = c(0, 1), labels = c(
                "Not Present", "Present"))

diam_init <- ggplot(analysis[diam_rows,], aes(x = InitialScouting)) +
                geom_bar(aes(y=(..count..)/(diam_games )), color=diam_col, fill=diam_col,
                alpha = 0.4) + labs(y=" ") + coord_cartesian(ylim =c(0, 1),xlim = c(-0.5,1.5))+
                scale_y_continuous(labels=scales::percent)+
                scale_x_continuous(name = "Diamond", breaks = c(0, 1), labels = c(
                "Not Present", "Present"))

mast_init <- ggplot(analysis[mast_rows,], aes(x = InitialScouting)) +
                geom_bar(aes(y=(..count..)/(mast_games )), color=mast_col, fill=mast_col,
                alpha = 0.4) + labs(y=" ") + coord_cartesian(ylim =c(0, 1),xlim = c(-0.5,1.5))+
                scale_y_continuous(labels=scales::percent)+
                scale_x_continuous(name = "Master", breaks = c(0, 1), labels = c(
                "Not Present", "Present"))

gmast_init <- ggplot(analysis[gmast_rows,], aes(x = InitialScouting)) +
                geom_bar(aes(y=(..count..)/(gmast_games )), color=gmast_col, fill=gmast_col,
                alpha = 0.4) + labs(y="% of Matches") + coord_cartesian(ylim =c(0, 1),xlim = c(-0.5,1.5))+
                scale_y_continuous(labels=scales::percent)+
                scale_x_continuous(name = "Grandmaster", breaks = c(0, 1), labels = c(
                "Not Present", "Present"))

title3 <- textGrob("Percentage of Matches with an Initial Scouting for each Rank",
                   gp=gpar(fontsize=11,font=3))

grid.arrange(bronze_init, silver_init, gold_init, plat_init, diam_init, mast_init, gmast_init, ncol=3, nrow=3, top = title3)
```

Same thing, but next to each other
```{r}
init_all_ranks <- ggplot(perc_rank, aes(x = Rank))+geom_col(aes(y=InitialScouting, fill=Rank), alpha=0.4) + 
            labs(y = "% of Matches with an Initial Scouting") +
            scale_y_continuous(labels=scales::percent) + 
            ggtitle("Percentage of Matches with an Initial Scouting for each Rank") +
            scale_fill_manual(values = rank_cols)
            
init_all_ranks
```

### Initial Scouting per Expertise
```{r}
novice_init <- ggplot(analysis[novice_rows,], aes(x = InitialScouting)) +
                geom_bar(aes(y=(..count..)/(novice_games)), color=novice_col, fill=novice_col,
                alpha = 0.4) + labs(y="% of Matches") + 
                coord_cartesian(ylim =c(0, 1),xlim = c(-0.5,1.5))+ 
                scale_y_continuous(labels=scales::percent)+
                scale_x_continuous(name = "Novice", breaks = c(0, 1), labels = c("Not Present",
                "Present"))

prof_init <- ggplot(analysis[prof_rows,], aes(x = InitialScouting)) +
                geom_bar(aes(y=(..count..)/(prof_games )), color=prof_col, fill=prof_col,
                alpha = 0.4) + labs(y=" ") + coord_cartesian(ylim =c(0, 1),xlim = c(-0.5,1.5))+
                scale_y_continuous(labels=scales::percent)+
                scale_x_continuous(name = "Proficient", breaks = c(0, 1), labels = c("Not Present",
                "Present"))

expert_init <- ggplot(analysis[expert_rows,], aes(x = InitialScouting)) +
                geom_bar(aes(y=(..count..)/(expert_games )), color=expert_col, fill=expert_col,
                alpha = 0.4) + labs(y=" ") + coord_cartesian(ylim =c(0, 1),xlim = c(-0.5,1.5))+
                scale_y_continuous(labels=scales::percent)+
                scale_x_continuous(name = "Expert", breaks = c(0, 1), labels = c("Not Present",
                "Present"))

title4 <- textGrob("Percentage of Players with an Initial Scouting for each Level of Expertise",
                   gp=gpar(fontsize=11,font=3))
grid.arrange(novice_init, prof_init, expert_init, ncol=3, nrow=1, top = title4)
```

Same thing, but next to each other
```{r}
init_all_expertise <- ggplot(perc_expertise, aes(x = Expertise))+geom_col(aes(y = InitialScouting,
            fill = Expertise), alpha = 0.4) + coord_cartesian(ylim =c(0, 1)) +
            labs(y = "% of Matches with an Initial Scouting") + scale_y_continuous(labels=scales::percent) + 
            ggtitle("Percentage of Matches with an Initial Scouting for each Level of Expertise") +
            scale_fill_manual(values = expertise_cols)
init_all_expertise
```

### Distribution of Base Scouting for each rank, normalized by % of Matches
```{r}
bronze_base <- ggplot(analysis[bronze_rows,], aes(x = BaseScouting)) +
                geom_bar(aes(y=(..count..)/(bronze_games)), color=bronze_col, fill=bronze_col,
                alpha = 0.4) + labs(y="% of Matches") + coord_cartesian(ylim =c(0,1),xlim=c(-1.5,1.5))+
                scale_y_continuous(labels=scales::percent)+
                scale_x_continuous(name = "Bronze", breaks = c(-1, 0, 1), labels = c("N/A", "Expansions",
                "Main"))

silver_base <- ggplot(analysis[silver_rows,], aes(x = BaseScouting)) +
                geom_bar(aes(y=(..count..)/(silver_games)), color=silver_col, fill=silver_col,
                alpha = 0.4) + labs(y=" ") + coord_cartesian(ylim =c(0, 1),xlim = c(-1.5,1.5))+
                scale_y_continuous(labels=scales::percent)+
                scale_x_continuous(name = "Silver", breaks = c(-1, 0, 1), labels = c("N/A", "Expansions",
                "Main"))

gold_base <- ggplot(analysis[gold_rows,], aes(x = BaseScouting)) +
                geom_bar(aes(y=(..count..)/(gold_games)), color=gold_col, fill=gold_col,
                alpha = 0.4) + labs(y=" ") + coord_cartesian(ylim =c(0, 1),xlim = c(-1.5,1.5))+
                scale_y_continuous(labels=scales::percent)+
                scale_x_continuous(name = "Gold", breaks = c(-1, 0, 1), labels = c("N/A", "Expansions",
                "Main"))

plat_base <- ggplot(analysis[plat_rows,], aes(x = BaseScouting)) +
              geom_bar(aes(y=(..count..)/(plat_games)), color=plat_col, fill=plat_col,
              alpha = 0.4) + labs(y="% of Matches") + coord_cartesian(ylim =c(0, 1),xlim = c(-1.5,1.5))+
              scale_y_continuous(labels=scales::percent)+
              scale_x_continuous(name = "Platinum", breaks = c(-1, 0, 1), labels = c("N/A", "Expansions",
                "Main"))

diam_base <- ggplot(analysis[diam_rows,], aes(x = BaseScouting)) +
              geom_bar(aes(y=(..count..)/(diam_games)), color=diam_col, fill=diam_col,
              alpha = 0.4) + labs(y=" ") + coord_cartesian(ylim =c(0, 1),xlim = c(-1.5,1.5))+
              scale_y_continuous(labels=scales::percent)+
              scale_x_continuous(name = "Diamond", breaks = c(-1, 0, 1), labels = c("N/A", "Expansions",
                "Main"))

mast_base <- ggplot(analysis[mast_rows,], aes(x = BaseScouting)) +
              geom_bar(aes(y=(..count..)/(mast_games)), color=mast_col, fill=mast_col,
              alpha = 0.4) + labs(y=" ") + coord_cartesian(ylim =c(0, 1),xlim = c(-1.5,1.5))+
              scale_y_continuous(labels=scales::percent)+
              scale_x_continuous(name = "Master", breaks = c(-1, 0, 1), labels = c("N/A", "Expansions",
                "Main"))

gmast_base <- ggplot(analysis[gmast_rows,], aes(x = BaseScouting)) +
              geom_bar(aes(y=(..count..)/(gmast_games)), color=gmast_col, fill=gmast_col,
              alpha = 0.4) + labs(y="% of Matches") + coord_cartesian(ylim =c(0, 1),xlim = c(-1.5,1.5))+
              scale_y_continuous(labels=scales::percent)+
              scale_x_continuous(name = "Grandmaster", breaks = c(-1, 0, 1), labels = c("N/A", "Expansions",
                "Main"))

title5 <- textGrob("Percentage of Matches where the Player Mostly Scouts their Opponent's Main Base, for each Rank",
                   gp=gpar(fontsize=11,font=3))

grid.arrange(bronze_base, silver_base, gold_base, plat_base, diam_base, mast_base, gmast_base, ncol=3, nrow=3, top = title5)
```

Same thing, but next to each other
```{r}
base_all_ranks <- ggplot(perc_rank, aes(x = Rank)) + geom_col(aes(y = Expansions, fill = Rank), alpha=0.4) +
                  labs(y = "% of Matches") + scale_y_continuous(labels=scales::percent) +
                  coord_cartesian(ylim =c(0, 1)) +
          ggtitle("Percentage of Matches where the Player Consistently Scouts their Opponent's Expansion Bases")+ theme(plot.title = element_text(size = 10)) + 
          scale_fill_manual(values = rank_cols)
base_all_ranks
```


### Base Scouting per Expertise
```{r}
novice_base <- ggplot(analysis[novice_rows,], aes(x = BaseScouting)) +
                geom_bar(aes(y=(..count..)/(novice_games)), color=novice_col, fill=novice_col,
                alpha = 0.4) + labs(y="% of Matches") + coord_cartesian(ylim =c(0, 1),xlim = c(-1.5,1.5))+
                scale_y_continuous(labels=scales::percent)+
                scale_x_continuous(name = "Novice", breaks = c(-1, 0, 1), labels = c("N/A", "Expansions",
                "Main"))

prof_base <- ggplot(analysis[prof_rows,], aes(x = BaseScouting)) +
                geom_bar(aes(y=(..count..)/(prof_games)), color=prof_col, fill=prof_col,
                alpha = 0.4) + labs(y=" ") + coord_cartesian(ylim =c(0, 1),xlim = c(-1.5,1.5))+
                scale_y_continuous(labels=scales::percent)+
                scale_x_continuous(name = "Proficient", breaks = c(-1, 0, 1), labels = c("N/A", "Expansions",
                "Main"))

expert_base <- ggplot(analysis[expert_rows,], aes(x = BaseScouting)) +
                geom_bar(aes(y=(..count..)/(expert_games)), color=expert_col, fill=expert_col,
                alpha = 0.4) + labs(y=" ") + coord_cartesian(ylim =c(0, 1),xlim = c(-1.5,1.5))+
                scale_y_continuous(labels=scales::percent)+
                scale_x_continuous(name = "Expert", breaks = c(-1, 0, 1), labels = c("N/A", "Expansions",
                "Main"))

title6 <- textGrob("Percentage of Matches where the Player Mostly Scouts their Opponent's Main Base, for each Level of Expertise",
                   gp=gpar(fontsize=9,font=3))
grid.arrange(novice_base, prof_base, expert_base, ncol=3, nrow=1, top = title6)
```

Same thing, but next to each other
```{r}
base_all_expertise <- ggplot(perc_expertise, aes(x=Expertise))+geom_col(aes(y = Expansions, fill=Expertise), 
            alpha = 0.4) + labs(y = "% of Matches") +
            scale_y_continuous(labels=scales::percent) + coord_cartesian(ylim =c(0, 1)) +
    ggtitle("Percentage of Matches where the Player Consistently Scouts their Opponent's Expansion Bases, per Expertise Level")+
    theme(plot.title = element_text(size = 10)) + scale_fill_manual(values = expertise_cols)
base_all_expertise
```

### Distribution of Scouting New Areas for each rank, normalized by % of Matches
```{r}
bronze_new <- ggplot(analysis[bronze_rows,], aes(x = NewAreas)) +
                geom_bar(aes(y=(..count..)/(bronze_games)), color=bronze_col, fill=bronze_col,
                alpha = 0.4) + labs(y="% of Matches") + coord_cartesian(ylim =c(0,1),xlim=c(-1.5,1.5))+
                scale_y_continuous(labels=scales::percent)+
                scale_x_continuous(name = "Bronze", breaks = c(-1, 0, 1), labels = c("N/A", "Same",
                "New"))

silver_new <- ggplot(analysis[silver_rows,], aes(x = NewAreas)) +
                geom_bar(aes(y=(..count..)/(silver_games)), color=silver_col, fill=silver_col,
                alpha = 0.4) + labs(y=" ") + coord_cartesian(ylim =c(0, 1),xlim = c(-1.5,1.5))+
                scale_y_continuous(labels=scales::percent)+
                scale_x_continuous(name = "Silver", breaks = c(-1, 0, 1), labels = c("N/A", "Same",
                "New"))

gold_new <- ggplot(analysis[gold_rows,], aes(x = NewAreas)) +
                geom_bar(aes(y=(..count..)/(gold_games)), color=gold_col, fill=gold_col,
                alpha = 0.4) + labs(y=" ") + coord_cartesian(ylim =c(0, 1),xlim = c(-1.5,1.5))+
                scale_y_continuous(labels=scales::percent)+
                scale_x_continuous(name = "Gold", breaks = c(-1, 0, 1), labels = c("N/A", "Same",
                "New"))

plat_new <- ggplot(analysis[plat_rows,], aes(x = NewAreas)) +
              geom_bar(aes(y=(..count..)/(plat_games)), color=plat_col, fill=plat_col,
              alpha = 0.4) + labs(y="% of Matches") + coord_cartesian(ylim =c(0, 1),xlim = c(-1.5,1.5))+
              scale_y_continuous(labels=scales::percent)+
              scale_x_continuous(name = "Platinum", breaks = c(-1, 0, 1), labels = c("N/A", "Same",
                "New"))

diam_new <- ggplot(analysis[diam_rows,], aes(x = NewAreas)) +
              geom_bar(aes(y=(..count..)/(diam_games)), color=diam_col, fill=diam_col,
              alpha = 0.4) + labs(y=" ") + coord_cartesian(ylim =c(0, 1),xlim = c(-1.5,1.5))+
              scale_y_continuous(labels=scales::percent)+
              scale_x_continuous(name = "Diamond", breaks = c(-1, 0, 1), labels = c("N/A", "Same",
                "New"))

mast_new <- ggplot(analysis[mast_rows,], aes(x = NewAreas)) +
              geom_bar(aes(y=(..count..)/(mast_games)), color=mast_col, fill=mast_col,
              alpha = 0.4) + labs(y=" ") + coord_cartesian(ylim =c(0, 1),xlim = c(-1.5,1.5))+
              scale_y_continuous(labels=scales::percent)+
              scale_x_continuous(name = "Master", breaks = c(-1, 0, 1), labels = c("N/A", "Same",
                "New"))

gmast_new <- ggplot(analysis[gmast_rows,], aes(x = NewAreas)) +
              geom_bar(aes(y=(..count..)/(gmast_games)), color=gmast_col, fill=gmast_col,
              alpha = 0.4) + labs(y="% of Matches") + coord_cartesian(ylim =c(0, 1),xlim = c(-1.5,1.5))+
              scale_y_continuous(labels=scales::percent)+
              scale_x_continuous(name = "Grandmaster", breaks = c(-1, 0, 1), labels = c("N/A", "Same",
                "New"))

title7 <- textGrob("Percentage of Matches where the Player Mostly Scouts New Areas, for each Rank",
                   gp=gpar(fontsize=11,font=3))

grid.arrange(bronze_new, silver_new, gold_new, plat_new, diam_new, mast_new, gmast_new, ncol=3, nrow=3, top = title7)
```

Same thing, but next to each other
```{r}
new_all_ranks <- ggplot(perc_rank, aes(x = Rank)) + geom_col(aes(y = NewAreas, fill=Rank), alpha = 0.4) +
            labs(y = "% of Matches") + scale_y_continuous(labels=scales::percent) + 
            coord_cartesian(ylim =c(0, 1)) +
    ggtitle("Percentage of Matches where the Player Consistently Scouts New Areas, for each Rank")+
            theme(plot.title = element_text(size = 10)) + scale_fill_manual(values = rank_cols)
new_all_ranks
```

### New Area Scouting per Expertise
```{r}
novice_new <- ggplot(analysis[novice_rows,], aes(x = NewAreas)) +
                geom_bar(aes(y=(..count..)/(novice_games)), color=novice_col, fill=novice_col,
                alpha = 0.4) + labs(y="% of Matches") + coord_cartesian(ylim =c(0, 1),xlim = c(-1.5,1.5))+
                scale_y_continuous(labels=scales::percent)+
                scale_x_continuous(name = "Novice", breaks = c(-1, 0, 1), labels = c("N/A", "Same",
                "New"))

prof_new <- ggplot(analysis[prof_rows,], aes(x = NewAreas)) +
                geom_bar(aes(y=(..count..)/(prof_games)), color=prof_col, fill=prof_col,
                alpha = 0.4) + labs(y=" ") + coord_cartesian(ylim =c(0, 1),xlim = c(-1.5,1.5))+
                scale_y_continuous(labels=scales::percent)+
                scale_x_continuous(name = "Proficient", breaks = c(-1, 0, 1), labels = c("N/A", "Same",
                "New"))

expert_new <- ggplot(analysis[expert_rows,], aes(x = NewAreas)) +
                geom_bar(aes(y=(..count..)/(expert_games)), color=expert_col, fill=expert_col,
                alpha = 0.4) + labs(y=" ") + coord_cartesian(ylim =c(0, 1),xlim = c(-1.5,1.5))+
                scale_y_continuous(labels=scales::percent)+
                scale_x_continuous(name = "Expert", breaks = c(-1, 0, 1), labels = c("N/A", "Same",
                "New"))

title8 <- textGrob("Percentage of Matches where the Player Mostly Scouts New Areas, for each Level of Expertise",
                   gp=gpar(fontsize=9,font=3))
grid.arrange(novice_new, prof_new, expert_new, ncol=3, nrow=1, top = title8)
```

Same thing, but next to each other
```{r}
new_all_expertise <- ggplot(perc_expertise, aes(x = Expertise))+geom_col(aes(y = NewAreas, fill=Expertise), 
            alpha = 0.4) + labs(y = "% of Matches") +
            scale_y_continuous(labels=scales::percent) + coord_cartesian(ylim =c(0, 1)) +
    ggtitle("Percentage of Matches where the Player Consistently Scouts New Areas, per Expertise Level")+
    theme(plot.title = element_text(size = 10)) + scale_fill_manual(values = expertise_cols)
new_all_expertise
```

### Distribution of Scouting Between Battles for each rank, normalized by % of Matches
```{r}
bronze_btwn <- ggplot(analysis[bronze_rows,], aes(x = BetweenBattles)) +
                geom_bar(aes(y=(..count..)/(bronze_games)), color=bronze_col, fill=bronze_col,
                alpha = 0.4) + labs(y="% of Matches") + coord_cartesian(ylim =c(0,1),xlim=c(-1.5,1.5))+
                scale_y_continuous(labels=scales::percent)+
                scale_x_continuous(name = "Bronze", breaks = c(-1, 0, 1), labels = c("N/A", "Incons.",
                "Cons."))

silver_btwn <- ggplot(analysis[silver_rows,], aes(x = BetweenBattles)) +
                geom_bar(aes(y=(..count..)/(silver_games)), color=silver_col, fill=silver_col,
                alpha = 0.4) + labs(y=" ") + coord_cartesian(ylim =c(0, 1),xlim = c(-1.5,1.5))+
                scale_y_continuous(labels=scales::percent)+
                scale_x_continuous(name = "Silver", breaks = c(-1, 0, 1), labels = c("N/A", "Incons.",
                "Cons."))

gold_btwn <- ggplot(analysis[gold_rows,], aes(x = BetweenBattles)) +
                geom_bar(aes(y=(..count..)/(gold_games)), color=gold_col, fill=gold_col,
                alpha = 0.4) + labs(y=" ") + coord_cartesian(ylim =c(0, 1),xlim = c(-1.5,1.5))+
                scale_y_continuous(labels=scales::percent)+
                scale_x_continuous(name = "Gold", breaks = c(-1, 0, 1), labels = c("N/A", "Incons.",
                "Cons."))

plat_btwn <- ggplot(analysis[plat_rows,], aes(x = BetweenBattles)) +
              geom_bar(aes(y=(..count..)/(plat_games)), color=plat_col, fill=plat_col,
              alpha = 0.4) + labs(y="% of Matches") + coord_cartesian(ylim =c(0, 1),xlim = c(-1.5,1.5))+
              scale_y_continuous(labels=scales::percent)+
              scale_x_continuous(name = "Platinum", breaks = c(-1, 0, 1), labels = c("N/A", "Incons.",
                "Cons."))

diam_btwn <- ggplot(analysis[diam_rows,], aes(x = BetweenBattles)) +
              geom_bar(aes(y=(..count..)/(diam_games)), color=diam_col, fill=diam_col,
              alpha = 0.4) + labs(y=" ") + coord_cartesian(ylim =c(0, 1),xlim = c(-1.5,1.5))+
              scale_y_continuous(labels=scales::percent)+
              scale_x_continuous(name = "Diamond", breaks = c(-1, 0, 1), labels = c("N/A", "Incons.",
                "Cons."))

mast_btwn <- ggplot(analysis[mast_rows,], aes(x = BetweenBattles)) +
              geom_bar(aes(y=(..count..)/(mast_games)), color=mast_col, fill=mast_col,
              alpha = 0.4) + labs(y=" ") + coord_cartesian(ylim =c(0, 1),xlim = c(-1.5,1.5))+
              scale_y_continuous(labels=scales::percent)+
              scale_x_continuous(name = "Master", breaks = c(-1, 0, 1), labels = c("N/A", "Incons.",
                "Cons."))

gmast_btwn <- ggplot(analysis[gmast_rows,], aes(x = BetweenBattles)) +
              geom_bar(aes(y=(..count..)/(gmast_games)), color=gmast_col, fill=gmast_col,
              alpha = 0.4) + labs(y="% of Matches") + coord_cartesian(ylim =c(0, 1),xlim = c(-1.5,1.5))+
              scale_y_continuous(labels=scales::percent)+
              scale_x_continuous(name = "Grandmaster", breaks = c(-1, 0, 1), labels = c("N/A", "Incons.",
                "Cons."))

title9 <- textGrob("Percentage of Matches where the Player Consistently Scouts Between Battles, for each Rank",
                   gp=gpar(fontsize=11,font=3))

grid.arrange(bronze_btwn, silver_btwn, gold_btwn, plat_btwn, diam_btwn, mast_btwn, gmast_btwn, ncol=3, nrow=3, top = title9)
```

Same thing, but next to each other
```{r}
btwn_all_ranks <- ggplot(perc_rank, aes(x = Rank)) + geom_col(aes(y = BetweenBattles, fill=Rank), 
            alpha = 0.4) + labs(y = "% of Matches") +
            scale_y_continuous(labels=scales::percent) + coord_cartesian(ylim =c(0, 1)) +
    ggtitle("Percentage of Matches where the Player Consistently Scouts Between Battles, for each Rank")+
    theme(plot.title = element_text(size = 10)) + scale_fill_manual(values = rank_cols)
btwn_all_ranks
```

### Base Scouting per Expertise
```{r}
novice_btwn <- ggplot(analysis[novice_rows,], aes(x = BetweenBattles)) +
                geom_bar(aes(y=(..count..)/(novice_games)), color=novice_col, fill=novice_col,
                alpha = 0.4) + labs(y="% of Matches") + coord_cartesian(ylim =c(0, 1),xlim = c(-1.5,1.5))+
                scale_y_continuous(labels=scales::percent)+
                scale_x_continuous(name = "Novice", breaks = c(-1, 0, 1), labels = c("N/A", "Incons.",
                "Cons."))

prof_btwn <- ggplot(analysis[prof_rows,], aes(x = BetweenBattles)) +
                geom_bar(aes(y=(..count..)/(prof_games)), color=prof_col, fill=prof_col,
                alpha = 0.4) + labs(y=" ") + coord_cartesian(ylim =c(0, 1),xlim = c(-1.5,1.5))+
                scale_y_continuous(labels=scales::percent)+
                scale_x_continuous(name = "Proficient", breaks = c(-1, 0, 1), labels = c("N/A", "Incons.",
                "Cons."))

expert_btwn <- ggplot(analysis[expert_rows,], aes(x = BetweenBattles)) +
                geom_bar(aes(y=(..count..)/(expert_games)), color=expert_col, fill=expert_col,
                alpha = 0.4) + labs(y=" ") + coord_cartesian(ylim =c(0, 1),xlim = c(-1.5,1.5))+
                scale_y_continuous(labels=scales::percent)+
                scale_x_continuous(name = "Expert", breaks = c(-1, 0, 1), labels = c("N/A", "Incons.",
                "Cons."))

title10 <- textGrob("Percentage of Matches where the Player Consistently Scouts Between Battles, for each Level of Expertise",
                   gp=gpar(fontsize=9,font=3))
grid.arrange(novice_btwn, prof_btwn, expert_btwn, ncol=3, nrow=1, top = title10)
```

Same thing, but next to each other
```{r}
btwn_all_expertise <- ggplot(perc_expertise, aes(x = Expertise))+geom_col(aes(y = BetweenBattles, 
            fill=Expertise), alpha = 0.4) + labs(y = "% of Matches") +
            scale_y_continuous(labels=scales::percent) + coord_cartesian(ylim =c(0, 1)) +
    ggtitle("Percentage of Matches where the Player Consistently Scouts Between Battles, per Expertise Level")+ theme(plot.title = element_text(size = 10))+ scale_fill_manual(values = expertise_cols)

btwn_all_expertise
```









