---
title: "Scouting Behavior Analysis"
author: "Alison Cameron"
date: "July 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
```

### Reading Data and Gathering Summary Statistics
```{r}
scouting <- read.csv("scouting_stats.csv")
summary(scouting)
scouting$Win2 <- ifelse(scouting$Win == 1, "win", "loss")
```

### Exploratory Data Analysis
```{r}
ggplot(scouting, aes(y=ScoutingFrequency, group=Win)) + geom_boxplot()
ggplot(scouting, aes(y=ScoutingTime, group=Win)) + geom_boxplot()
ggplot(scouting, aes(x = Win, y = ScoutingTime, color = Win2, shape = Win2)) + geom_point()
ggplot(scouting, aes(x = Win, y = ScoutingFrequency, color = Win2, shape = Win2)) + geom_point()
```

### Creating a Binary Logistic Regression Model
```{r}
scouting.glm <- glm(Win ~ ScoutingTime + ScoutingFrequency, data = scouting, family = binomial)
summary(scouting.glm)
```

Checking if one variable is more significant than the other
```{r}
scouting.glm2 <- update(scouting.glm, . ~ . -ScoutingFrequency)
summary(scouting.glm2)
anova(scouting.glm2, scouting.glm, test = "Chisq")
```

```{r}
scouting.glm3 <- update(scouting.glm, . ~ . -ScoutingTime)
summary(scouting.glm3)
anova(scouting.glm3, scouting.glm, test = "Chisq")
```

ScoutingTime appears to be much more significant than ScoutingFrequency. 
Therefore, we accept scouting.glm2 to be the more accurate model.

### Interpretation
```{r}
oddsIncrease <- exp(7.20713*log(1.1))
oddsIncrease
```

For a 10% increase in the time spent scouting an opponent, the odds that a player will win
increases by a factor of 1.987



