---
title: "Scouting Distribution"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(ggthemes)
library(scales)
library(grid)
library(gridExtra)
library(dplyr)
```

### Reading data
```{r}
#csvs produced by running scouting_time.py
time_fracs <- read.csv("scouting_time_fraction.csv")
time_frames1 <- read.csv("scouting_time_frames1.csv")
```


```{r}
time_fracs$Expertise <- ifelse(time_fracs$Rank == 1, 1, ifelse(time_fracs$Rank == 2,
                      1, ifelse(time_fracs$Rank == 3, -1, ifelse(time_fracs$Rank == 4,
                      2, ifelse(time_fracs$Rank == 5, 2, ifelse(time_fracs$Rank
                      == 6, -1, ifelse(time_fracs$Rank ==7, 3, 0)))))))

time_frames1$Expertise <- ifelse(time_frames1$Rank == 1, 1, ifelse(time_frames1$Rank == 2,
                      1, ifelse(time_frames1$Rank == 3, -1, ifelse(time_frames1$Rank == 4,
                      2, ifelse(time_frames1$Rank == 5, 2, ifelse(time_frames1$Rank
                      == 6, -1, ifelse(time_frames1$Rank ==7, 3, 0)))))))
```

```{r}
bronze_fracs <- which(time_fracs$Rank == 1)
silver_fracs <- which(time_fracs$Rank == 2)
gold_fracs <- which(time_fracs$Rank == 3)
plat_fracs <- which(time_fracs$Rank == 4)
diam_fracs <- which(time_fracs$Rank == 5)
master_fracs <- which(time_fracs$Rank == 6)
gmaster_fracs <- which(time_fracs$Rank == 7)

novice_fracs <- which(time_fracs$Expertise == 1)
prof_fracs <- which(time_fracs$Expertise == 2)
expert_fracs <- which(time_fracs$Expertise == 3)

bronze_frames <- which(time_frames1$Rank == 1)
silver_frames <- which(time_frames1$Rank == 2)
gold_frames <- which(time_frames1$Rank == 3)
plat_frames <- which(time_frames1$Rank == 4)
diam_frames <- which(time_frames1$Rank == 5)
master_frames <- which(time_frames1$Rank == 6)
gmaster_frames <- which(time_frames1$Rank == 7)

novice_frames <- which(time_frames1$Expertise == 1)
prof_frames <- which(time_frames1$Expertise == 2)
expert_frames <- which(time_frames1$Expertise == 3)

#these numbers are obtained from the terminal output when running data_diagnosis.match_counter("scouting_time_fraction.csv")
bronze_uids <- 782
silver_uids <- 6212
gold_uids <- 10732
plat_uids <- 21034
diam_uids <- 26675
mast_uids <- 7732
gmast_uids <- 2507

novice_uids <- bronze_uids + silver_uids
prof_uids <- plat_uids + diam_uids
expert_uids <- gmast_uids
```

```{r}
bronze_col <- "#4d4dff"
silver_col <- "#36b3b3"
gold_col <- "#884dff"
plat_col <- "#00e5e6"
diam_col <- "#3655b3"
mast_col <- "#000066"
gmast_col <- "#3c00b3"

novice_col <- "#4d4dff"
prof_col <- "#36b3b3"
expert_col <- "#884dff"
```

### Distribution of scouting by fraction of game time for each rank, Normalized by % of Scouting instances
```{r}
bronze_fracs_hist <- ggplot(time_fracs[bronze_fracs,], aes(x = ScoutTime)) +
              geom_histogram(aes(y=(..count..)/length(bronze_fracs)),color=bronze_col, fill=bronze_col,
                bins = 20, alpha = 0.6) + labs(y="% of Scouting", x = "Gametime-Bronze") + 
                coord_cartesian(ylim =c(0, 0.12)) + scale_y_continuous(labels=scales::percent) +
                scale_x_continuous(labels = scales::percent)

silver_fracs_hist <- ggplot(time_fracs[silver_fracs,], aes(x = ScoutTime)) +
              geom_histogram(aes(y=(..count..)/length(silver_fracs)),color=silver_col,fill=silver_col,
                bins = 20, alpha = 0.4)+ labs(y = " ", x = "Gametime-Silver") + 
                coord_cartesian(ylim = c(0, 0.12))+ scale_y_continuous(labels=scales::percent) +
                scale_x_continuous(labels = scales::percent)

gold_fracs_hist <- ggplot(time_fracs[gold_fracs,], aes(x = ScoutTime)) +
                geom_histogram(aes(y=(..count..)/length(gold_fracs)),color=gold_col,fill=gold_col,
                bins = 20, alpha = 0.4)+ labs(y = " ", x = "Gametime-Gold") + 
                coord_cartesian(ylim = c(0, 0.12))+ scale_y_continuous(labels=scales::percent) +
                scale_x_continuous(labels = scales::percent)

plat_fracs_hist <- ggplot(time_fracs[plat_fracs,], aes(x = ScoutTime)) +
                geom_histogram(aes(y=(..count..)/length(plat_fracs)),color=plat_col,fill=plat_col,
                bins = 20, alpha = 0.4)+labs(y="% of Scouting", x = "Gametime-Platinum") + 
                coord_cartesian(ylim = c(0, 0.12))+ scale_y_continuous(labels=scales::percent) +
                scale_x_continuous(labels = scales::percent)

diam_fracs_hist <- ggplot(time_fracs[diam_fracs,], aes(x = ScoutTime)) +
                geom_histogram(aes(y=(..count..)/length(diam_fracs)),color=diam_col,fill=diam_col,
                bins = 20, alpha = 0.4)+ labs(y = " ", x = "Gametime-Diamond") + 
                coord_cartesian(ylim = c(0, 0.12))+ scale_y_continuous(labels=scales::percent) +
                scale_x_continuous(labels = scales::percent)

mast_fracs_hist <- ggplot(time_fracs[master_fracs,], aes(x = ScoutTime)) +
                geom_histogram(aes(y=(..count..)/length(master_fracs)),color=mast_col,fill=mast_col,
                bins = 20, alpha = 0.4)+ labs(y=" ", x = "Gametime-Master") + 
                coord_cartesian(ylim = c(0, 0.12))+ scale_y_continuous(labels=scales::percent) +
                scale_x_continuous(labels = scales::percent)

gmaster_fracs_hist <- ggplot(time_fracs[gmaster_fracs,], aes(x = ScoutTime)) +
                geom_histogram(aes(y=(..count..)/length(gmaster_fracs)),color=gmast_col,fill=gmast_col,
                bins = 20, alpha = 0.4)+labs(y = "% of Scouting", x="Gametime-Grandmaster") +
                coord_cartesian(ylim = c(0, 0.12))+ scale_y_continuous(labels=scales::percent) +
                scale_x_continuous(labels = scales::percent)

title <- textGrob("Percentage of Scouting Instances for Fraction of Gametime, separated by Rank",
                  gp=gpar(fontsize=14,font=3))

grid.arrange(bronze_fracs_hist, silver_fracs_hist, gold_fracs_hist, plat_fracs_hist, diam_fracs_hist, mast_fracs_hist, gmaster_fracs_hist, ncol=3, nrow=3, top = title)
```

### Distribution of scouting by fraction of game time for expertise, normalized by % of Scouting instances
```{r}
novice_fracs_hist <- ggplot(time_fracs[novice_fracs,], aes(x = ScoutTime)) +
              geom_histogram(aes(y=(..count..)/length(novice_fracs)),color=novice_col, fill=novice_col,
                bins = 20, alpha = 0.4) + labs(y="% of Scouting", x = "Gametime-Novice") + 
                coord_cartesian(ylim =c(0, 0.12))+ scale_y_continuous(labels=scales::percent) +
                scale_x_continuous(labels = scales::percent)
prof_fracs_hist <- ggplot(time_fracs[prof_fracs,], aes(x = ScoutTime)) +
                geom_histogram(aes(y=(..count..)/length(prof_fracs)),color=prof_col,fill=prof_col,
                bins = 20, alpha = 0.4)+ labs(y = " ", x = "Gametime-Proficient") + 
                coord_cartesian(ylim = c(0, 0.12))+ scale_y_continuous(labels=scales::percent) +
                scale_x_continuous(labels = scales::percent)
expert_fracs_hist <- ggplot(time_fracs[expert_fracs,], aes(x = ScoutTime)) +
              geom_histogram(aes(y=(..count..)/length(expert_fracs)),color=expert_col,fill=expert_col,
                bins = 20, alpha = 0.4)+ labs(y = " ", x = "Gametime-Expert") + 
                coord_cartesian(ylim = c(0, 0.12))+ scale_y_continuous(labels=scales::percent) +
                scale_x_continuous(labels = scales::percent)
title2 <- textGrob("Percentage of Scouting Instances for Fraction of Gametime, separated by Expertise",
                  gp=gpar(fontsize=13,font=3))

grid.arrange(novice_fracs_hist, prof_fracs_hist, expert_fracs_hist, ncol=3, nrow=1, top = title2)
```

### Distribution of scouting by fraction of game time for each rank, normalized by % of matches
```{r}
bronze_fracs_hist2 <- ggplot(time_fracs[bronze_fracs,], aes(x = ScoutTime)) +
                geom_histogram(aes(y=(..count..)/(bronze_uids)), color=bronze_col, fill=bronze_col,
                bins = 35, alpha = 0.4) + labs(y="% of Matches", x = "Gametime-Bronze") + 
                coord_cartesian(ylim =c(0, 1))+ scale_y_continuous(labels=scales::percent) +
                scale_x_continuous(labels = scales::percent)
silver_fracs_hist2 <- ggplot(time_fracs[silver_fracs,], aes(x = ScoutTime)) +
                geom_histogram(aes(y=(..count..)/(silver_uids)),color=silver_col,fill=silver_col,
                bins = 35, alpha = 0.4)+ labs(y = " ", x = "Gametime-Silver") + 
                coord_cartesian(ylim = c(0, 1))+ scale_y_continuous(labels=scales::percent) +
                scale_x_continuous(labels = scales::percent)
gold_fracs_hist2 <- ggplot(time_fracs[gold_fracs,], aes(x = ScoutTime)) +
                geom_histogram(aes(y=(..count..)/(gold_uids)),color=gold_col,fill=gold_col,
                bins = 35, alpha = 0.4)+ labs(y = " ", x = "% of Gametime-Gold") + 
                coord_cartesian(ylim = c(0, 1))+ scale_y_continuous(labels=scales::percent) +
                scale_x_continuous(labels = scales::percent)
plat_fracs_hist2 <- ggplot(time_fracs[plat_fracs,], aes(x = ScoutTime)) +
                geom_histogram(aes(y=(..count..)/(plat_uids)),color=plat_col,fill=plat_col,
                bins = 35, alpha = 0.4)+labs(y="% of Matches", x = "Gametime-Platinum") + 
                coord_cartesian(ylim = c(0, 1))+ scale_y_continuous(labels=scales::percent) +
                scale_x_continuous(labels = scales::percent)
diam_fracs_hist2 <- ggplot(time_fracs[diam_fracs,], aes(x = ScoutTime)) +
                geom_histogram(aes(y=(..count..)/(diam_uids)),color=diam_col,fill=diam_col,
                bins = 35, alpha = 0.4)+ labs(y = " ", x = "Gametime-Diamond") + 
                coord_cartesian(ylim = c(0, 1))+ scale_y_continuous(labels=scales::percent) +
                scale_x_continuous(labels = scales::percent)
mast_fracs_hist2 <- ggplot(time_fracs[master_fracs,], aes(x = ScoutTime)) +
                geom_histogram(aes(y=(..count..)/(mast_uids)),color=mast_col,fill=mast_col,
                bins = 35, alpha = 0.4)+ labs(y=" ", x = "Gametime-Master") + 
                coord_cartesian(ylim = c(0, 1))+ scale_y_continuous(labels=scales::percent) +
                scale_x_continuous(labels = scales::percent)
gmaster_fracs_hist2 <- ggplot(time_fracs[gmaster_fracs,], aes(x = ScoutTime)) +
                geom_histogram(aes(y=(..count..)/(gmast_uids)),color=gmast_col,fill=gmast_col,
                bins = 35, alpha = 0.4)+labs(y = "% of Matches", x="Gametime-Grandmaster") +
                coord_cartesian(ylim = c(0, 1))+ scale_y_continuous(labels=scales::percent) +
                scale_x_continuous(labels = scales::percent)

title3 <- textGrob("Percentage of Matches where Scouting Ocurred at each Fraction of Gametime, separated by Rank",
                   gp=gpar(fontsize=11,font=3))

grid.arrange(bronze_fracs_hist2, silver_fracs_hist2, gold_fracs_hist2, plat_fracs_hist2, diam_fracs_hist2, mast_fracs_hist2, gmaster_fracs_hist2, ncol=3, nrow=3, top = title3)
```

### Distribution of scouting by fraction of game time for expertise, normalized by % of matches
```{r}
novice_fracs_hist2 <- ggplot(time_fracs[novice_fracs,], aes(x = ScoutTime)) +
                geom_histogram(aes(y=(..count..)/(novice_uids)), color=novice_col, fill=novice_col,
                bins = 35, alpha = 0.4) + labs(y="% of Matches", x = "Gametime-Novice") + 
                coord_cartesian(ylim =c(0, 1))+ scale_y_continuous(labels=scales::percent) +
                scale_x_continuous(labels = scales::percent)
prof_fracs_hist2 <- ggplot(time_fracs[prof_fracs,], aes(x = ScoutTime)) +
                geom_histogram(aes(y=(..count..)/(prof_uids)),color=prof_col,fill=prof_col,
                bins = 35, alpha = 0.4)+ labs(y = " ", x = "Gametime-Proficient") + 
                coord_cartesian(ylim = c(0, 1))+ scale_y_continuous(labels=scales::percent) +
                scale_x_continuous(labels = scales::percent)
expert_fracs_hist2 <- ggplot(time_fracs[expert_fracs,], aes(x = ScoutTime)) +
                geom_histogram(aes(y=(..count..)/(expert_uids)),color=expert_col,fill=expert_col,
                bins = 35, alpha = 0.4)+ labs(y = " ", x = "Gametime-Expert") + 
                coord_cartesian(ylim = c(0, 1))+ scale_y_continuous(labels=scales::percent) +
                scale_x_continuous(labels = scales::percent)
title4 <- textGrob("Percentage of Matches where Scouting Ocurred at each Fraction of Gametime, separated by Expertise",
                   gp=gpar(fontsize=11,font=3))
grid.arrange(novice_fracs_hist2, prof_fracs_hist2, expert_fracs_hist2, ncol=3, nrow=1, top = title4)
```

### Distribution of scouting by frames for each rank, Normalized by # of scouting instances
```{r}
bronze_frames_hist <- ggplot(time_frames1[bronze_frames,], aes(x = ScoutTime)) +
              geom_histogram(aes(y=(..count..)/length(bronze_frames)),color=bronze_col,fill=bronze_col,
                bins = 20, binwidth =4000, alpha = 0.4) + labs(y="% of Scouting", x="Frames-Bronze") +
                coord_cartesian(ylim =c(0, 0.5), xlim = c(0, 65000))+
                scale_y_continuous(labels=scales::percent)

silver_frames_hist <- ggplot(time_frames1[silver_frames,], aes(x = ScoutTime)) +
              geom_histogram(aes(y=(..count..)/length(silver_frames)),color=silver_col,fill=silver_col,
                bins = 20, binwidth = 4000, alpha = 0.4)+ labs(y = " ", x = "Frames-Silver") + 
                coord_cartesian(ylim = c(0, 0.5), xlim = c(0, 65000))+
                scale_y_continuous(labels=scales::percent)

gold_frames_hist <- ggplot(time_frames1[gold_frames,], aes(x = ScoutTime)) +
                geom_histogram(aes(y=(..count..)/length(gold_frames)),color=gold_col,fill=gold_col,
                bins = 20, binwidth = 4000, alpha = 0.4)+ labs(y = " ", x = "Frames-Gold") + 
                coord_cartesian(ylim = c(0, 0.5), xlim = c(0, 65000))+
                scale_y_continuous(labels=scales::percent)

plat_frames_hist <- ggplot(time_frames1[plat_frames,], aes(x = ScoutTime)) +
                geom_histogram(aes(y=(..count..)/length(plat_frames)),color=plat_col,fill=plat_col,
                bins = 20, binwidth = 4000, alpha = 0.4)+labs(y="% of Scouting", x="Frames-Platinum") +
                coord_cartesian(ylim = c(0, 0.5), xlim = c(0, 65000))+
                scale_y_continuous(labels=scales::percent)

diam_frames_hist <- ggplot(time_frames1[diam_frames,], aes(x = ScoutTime)) +
                geom_histogram(aes(y=(..count..)/length(diam_frames)),color=diam_col,fill=diam_col,
                bins = 20, binwidth = 4000, alpha = 0.4)+ labs(y = " ", x = "Frames-Diamond") + 
                coord_cartesian(ylim = c(0, 0.5), xlim = c(0, 65000))+
                scale_y_continuous(labels=scales::percent)

mast_frames_hist <- ggplot(time_frames1[master_frames,], aes(x = ScoutTime)) +
                geom_histogram(aes(y=(..count..)/length(master_frames)),color=mast_col,fill=mast_col,
                bins = 20, binwidth = 4000, alpha = 0.4)+ labs(y=" ", x="Frames-Master") + 
                coord_cartesian(ylim = c(0, 0.5), xlim = c(0, 65000))+
                scale_y_continuous(labels=scales::percent)

gmaster_frames_hist <- ggplot(time_frames1[gmaster_frames,], aes(x = ScoutTime)) +
              geom_histogram(aes(y=(..count..)/length(gmaster_frames)),color=gmast_col,fill=gmast_col,
                bins = 20, binwidth = 4000, alpha = 0.4)+labs(y = "% of Scouting", x="Frames-Grandmaster") +
                coord_cartesian(ylim = c(0, 0.5), xlim = c(0, 65000))+
                scale_y_continuous(labels=scales::percent)


title5 <- textGrob("Percentage of Scouting Instances for each Frame, separated by Rank",
                   gp=gpar(fontsize=14,font=3))

grid.arrange(bronze_frames_hist, silver_frames_hist, gold_frames_hist, plat_frames_hist, diam_frames_hist, mast_frames_hist, gmaster_frames_hist, ncol=3, nrow=3, top = title5)
```

### Distribution of scouting by frames for expertise, Normalized by # of scouting instances
```{r}
novice_frames_hist <- ggplot(time_frames1[novice_frames,], aes(x = ScoutTime)) +
              geom_histogram(aes(y=(..count..)/length(novice_frames)),color=novice_col,fill=novice_col,
                bins = 20, binwidth = 4000, alpha=0.4) + labs(y="% of Scouting", x="Frames-Novice") + 
                coord_cartesian(ylim =c(0, 0.5), xlim = c(0, 65000))+
                scale_y_continuous(labels=scales::percent)
prof_frames_hist <- ggplot(time_frames1[prof_frames,], aes(x = ScoutTime)) +
                geom_histogram(aes(y=(..count..)/length(prof_frames)), color=prof_col, fill=prof_col,
                bins = 20, binwidth = 4000, alpha = 0.4) + labs(y=" ", x = "Frames-Proficient") + 
                coord_cartesian(ylim =c(0, 0.5), xlim = c(0, 65000))+
                scale_y_continuous(labels=scales::percent)
expert_frames_hist <- ggplot(time_frames1[expert_frames,], aes(x = ScoutTime)) +
              geom_histogram(aes(y=(..count..)/length(expert_frames)),color=expert_col,fill=expert_col,
                bins = 20, binwidth = 4000, alpha = 0.4) + labs(y=" ", x = "Frames-Expert") + 
                coord_cartesian(ylim =c(0, 0.5), xlim = c(0, 65000))+
                scale_y_continuous(labels=scales::percent)
title6 <- textGrob("Percentage of Scouting Instances for each Frame, separated by Expertise",
                   gp=gpar(fontsize=14,font=3))
grid.arrange(novice_frames_hist, prof_frames_hist, expert_frames_hist, ncol=3, nrow=1, top = title6)
```

### Distribution of scouting by frames for each rank, Normalized by % of matches
```{r}
bronze_frames_hist2 <- ggplot(time_frames1[bronze_frames,], aes(x = ScoutTime)) +
                geom_histogram(aes(y=(..count..)/(bronze_uids)), color=bronze_col, fill=bronze_col,
                binwidth = 400, alpha = 0.4) + labs(y="% of Matches", x = "Frames-Bronze") + 
                coord_cartesian(ylim =c(0, 1), xlim = c(0, 40000))+
                scale_y_continuous(labels=scales::percent)
silver_frames_hist2 <- ggplot(time_frames1[silver_frames,], aes(x = ScoutTime)) +
                geom_histogram(aes(y=(..count..)/(silver_uids)), color=silver_col, fill=silver_col,
                binwidth = 400, alpha = 0.4) + labs(y=" ", x = "Frames-Silver") + 
                coord_cartesian(ylim =c(0, 1), xlim = c(0, 40000))+
                scale_y_continuous(labels=scales::percent)
gold_frames_hist2 <- ggplot(time_frames1[gold_frames,], aes(x = ScoutTime)) +
                geom_histogram(aes(y=(..count..)/(gold_uids)), color=gold_col, fill=gold_col,
                binwidth = 400, alpha = 0.4) + labs(y=" ", x = "Frames-Gold") + 
                coord_cartesian(ylim =c(0, 1), xlim = c(0, 40000))+
                scale_y_continuous(labels=scales::percent)
plat_frames_hist2 <- ggplot(time_frames1[plat_frames,], aes(x = ScoutTime)) +
                geom_histogram(aes(y=(..count..)/(plat_uids)), color=plat_col, fill=plat_col,
                binwidth = 400, alpha = 0.4) + labs(y="% of Matches", x = "Frames-Platinum") + 
                coord_cartesian(ylim =c(0, 1), xlim = c(0, 40000))+
                scale_y_continuous(labels=scales::percent)
diam_frames_hist2 <- ggplot(time_frames1[diam_frames,], aes(x = ScoutTime)) +
                geom_histogram(aes(y=(..count..)/(diam_uids)), color=diam_col, fill=diam_col,
                binwidth = 400, alpha = 0.4) + labs(y=" ", x = "Frames-Diamond") + 
                coord_cartesian(ylim =c(0, 1), xlim = c(0, 40000))+
                scale_y_continuous(labels=scales::percent)
mast_frames_hist2 <- ggplot(time_frames1[master_frames,], aes(x = ScoutTime)) +
                geom_histogram(aes(y=(..count..)/(mast_uids)), color=mast_col, fill=mast_col,
                binwidth = 400, alpha = 0.4) + labs(y=" ", x = "Frames-Master") + 
                coord_cartesian(ylim =c(0, 1), xlim = c(0, 40000))+
                scale_y_continuous(labels=scales::percent)
gmaster_frames_hist2 <- ggplot(time_frames1[gmaster_frames,], aes(x = ScoutTime)) +
                geom_histogram(aes(y=(..count..)/(gmast_uids)), color=gmast_col, fill=gmast_col,
                binwidth = 400, alpha = 0.4) + labs(y="% of Matches", x = "Frames-Grandmaster") + 
                coord_cartesian(ylim =c(0, 1), xlim = c(0, 40000))+
                scale_y_continuous(labels=scales::percent)
title7 <- textGrob("Percentage of Matches where Scouting Ocurred at each Frame, separated by Rank",
                   gp=gpar(fontsize=11,font=3))
grid.arrange(bronze_frames_hist2, silver_frames_hist2, gold_frames_hist2, plat_frames_hist2, diam_frames_hist2, mast_frames_hist2, gmaster_frames_hist2, ncol=3, nrow=3, top = title7)
```

### Distribution of scouting by frames for each rank, Normalized by % of matches
```{r}
novice_frames_hist2 <- ggplot(time_frames1[novice_frames,], aes(x = ScoutTime)) +
                geom_histogram(aes(y=(..count..)/(novice_uids)), color=novice_col, fill=novice_col,
                binwidth = 400, alpha = 0.4) + labs(y="% of Matches", x = "Frames-Novice") + 
                coord_cartesian(ylim =c(0, 1), xlim = c(0, 40000))+
                scale_y_continuous(labels=scales::percent)
prof_frames_hist2 <- ggplot(time_frames1[prof_frames,], aes(x = ScoutTime)) +
                geom_histogram(aes(y=(..count..)/(prof_uids)), color=prof_col, fill=prof_col,
                binwidth = 400, alpha = 0.4) + labs(y=" ", x = "Frames-Proficient") + 
                coord_cartesian(ylim =c(0, 1), xlim = c(0, 40000))+
                scale_y_continuous(labels=scales::percent)
expert_frames_hist2 <- ggplot(time_frames1[expert_frames,], aes(x = ScoutTime)) +
                geom_histogram(aes(y=(..count..)/(expert_uids)), color=expert_col, fill=expert_col,
                binwidth = 400, alpha = 0.4) + labs(y=" ", x = "Frames-Expert") + 
                coord_cartesian(ylim =c(0, 1), xlim = c(0, 40000))+
                scale_y_continuous(labels=scales::percent)

title8 <- textGrob("Percentage of Matches where Scouting Ocurred at each Frame, separated by Expertise",
                   gp=gpar(fontsize=11,font=3))
grid.arrange(novice_frames_hist2, prof_frames_hist2, expert_frames_hist2, ncol=3, nrow=1, top = title8)
```






